The \proglang{R} Package \pkg{forestinventory}: Design-Based Global and Small Area Estimations for Multi-Phase Forest Inventories

### 2017-10-27 rnw/Calculation of Confidence Intervals.Rnw
formatting revision (4)

Based on the central limit theorem it can be assumed that under hypothetical repeated sampling the point estimates will asymptotically follow a normal distribution. However, on the recommendation of \citet{mandallaz2013a}, better confidence intervals can obtained using the Student's \textit{t} distribution (\citet{mandallaz2013a}) defined as

>>>>

Based on the central limit theorem it can be assumed that under hypothetical repeated sampling the point estimates will asymptotically follow a normal distribution. However, on the recommendation of \citet{mandallaz2013a}, better confidence intervals can obtained using the Student's \textit{t} distribution defined as

### 2017-10-27 rnw/Introduction.Rnw
formatting revision (4)

Terrestrial inventories have the benefit of being very flexible in the sense that they can be used to produce high quality estimates for a wide-variety of different forest attributes. However, they have the downside of being very expensive.  Improving the precision of the estimates by increasing the number of sample plots essentially means that travel costs will rise as trained inventorists are sent to more and more plot locations. This is why the number of terrestrial samples is often limited. Although national inventories usually possess a sufficiently large terrestrial sample size to provide high estimation accuracies for larger areas, this is often not the case for smaller areas, such as forest management units.  As a result, there has been an increasing need for alternative inventory methods that can maintain the same estimation precision at lower costs, or achieve higher estimation precision at identical costs \citep{vonluepke2013}. A method which has become particularly attractive is called multi-phase sampling. The core concept is to enlarge the sample size in order to gain higher estimation precision without enlarging the terrestrial sample size. This is done by using predictions of the terrestrial target variable at additional sample locations where the terrestrial information has not been gathered. These predictions are produced by regression models that use explanatory variables derived from auxiliary
data, commonly in the form of spatially exhaustive remote sensing data in the inventory area. Regression estimators using this concept can consider either one additional sample of plot locations consisting of auxiliary information (two-phase or double-sampling) or two additional samples available in different sample sizes (three-phase or triple-sampling) \citep{gregoire2007, saborowski2010, mandallaz2013a, mandallaz2013c, vonLüpke2012}. Their application to existing forest inventory systems have already showed their efficiency in terms of cost reduction and gain in estimation precision \citep{breidenbach2012, vonLuebke2014, mandallaz2013b, magnussen2014, massey2014a}.\par

@@

Commercial as well as open-source software already implement multi-stage and multi-phase estimation, such as the survey sampling procedures in \proglang{SAS} \citep{sas} and the \pkg{survey} package in \proglang{R} \citep{survey}. However, both are targeted towards list-sampling as it is applied in official statistics. Available software providing multi-phase sampling methods better suited for forest inventories has been rare. Two exceptions are the \proglang{R} package \pkg{JoSAE} by \citet{josae2015} and the package \pkg{maSAE} by \citet{cullmann2016}. However, a more comprehensive software package covering a larger variety of sample designs and estimators for forest inventories has not yet been available, which is the motivation behind the \proglang{R} package \pkg{forestinventory}. The package provides global and small area estimators for two-phase and three-phase forest inventories under simple and cluster sampling, which have been developed under the infinite population approach by Daniel Mandallaz at ETH Zurich between 2008 and 2017. The implemented methods have been demonstrated by case studies in Switzerland \citep{massey2014a, massey2015b, mandallaz2013b} and Germany \citep{hill2017a}. The implemented estimators cover 32 inventory scenarios and can be used for post-stratification, regression and regression within strata \citep{massey2015}. The long-term objective of \pkg{forestinventory} is to make the broad range of estimators available to a large user community and to facilitate their application in science as well as operational forest management.

>>>>

Terrestrial inventories have the benefit of being very flexible in the sense that they can be used to produce high quality estimates for a wide-variety of different forest attributes. However, they have the downside of being very expensive.  Improving the precision of the estimates by increasing the number of sample plots essentially means that travel costs will rise as trained inventorists are sent to more and more plot locations. This is why the number of terrestrial samples is often limited. Although national inventories usually possess a sufficiently large terrestrial sample size to provide high estimation accuracies for larger areas, this is often not the case for smaller areas, such as forest management units.  As a result, there has been an increasing need for alternative inventory methods that can maintain the same estimation precision at lower costs, or achieve higher estimation precision at identical costs \citep{vonluepke2013}. A method which has become particularly attractive is called multi-phase sampling. The core concept is to enlarge the sample size in order to gain higher estimation precision without enlarging the terrestrial sample size. This is done by using predictions of the terrestrial target variable at additional sample locations where the terrestrial information has not been gathered. These predictions are produced by regression models that use explanatory variables derived from auxiliary
data, commonly in the form of spatially exhaustive remote sensing data in the inventory area. Regression estimators using this concept can consider either one additional sample of plot locations (two-phase or double-sampling) or two additional samples available in different sample sizes (three-phase or triple-sampling) \citep{gregoire2007, saborowski2010, mandallaz2013a, mandallaz2013c, vonLüpke2012}. Their application to existing forest inventory systems have already showed their efficiency in terms of cost reduction and gain in estimation precision \citep{breidenbach2012, vonLuebke2014, mandallaz2013b, magnussen2014, massey2014a}.\par

@@

Multi-stage and multi-phase estimation has already been implemented in commercial as well as open-source software, such as the survey sampling procedures in \proglang{SAS} \citep{sas} and the \pkg{survey} package in \proglang{R} \citep{survey}. However, both are targeted towards list-sampling as it is applied in official statistics. Available software providing multi-phase sampling methods better suited for forest inventories has been rare. Two exceptions are the \proglang{R} package \pkg{JoSAE} by \citet{josae2015} and the \pkg{maSAE} package by \citet{cullmann2016}. However, a more comprehensive software package covering a larger variety of sample designs and estimators for forest inventories has not yet been available, which is the motivation behind the \proglang{R} package \pkg{forestinventory}. The package provides global and small area estimators for two-phase and three-phase forest inventories under simple and cluster sampling, which have been developed under the infinite population approach by Daniel Mandallaz at ETH Zurich between 2008 and 2017. The implemented methods have been demonstrated by case studies in Switzerland \citep{massey2014a, massey2015b, mandallaz2013b} and Germany \citep{hill2017a}. The implemented estimators cover 32 inventory scenarios and can be used for post-stratification, regression and regression within strata \citep{massey2015}. The long-term objective of \pkg{forestinventory} is to make the broad range of estimators available to a large user community and to facilitate their application in science as well as operational forest management.

### 2017-10-27 rnw/Main structure and modules of the Package.Rnw
formatting revision (4)

Most forest inventories gather terrestrial information by sending field crews to randomly (or systematically) selected points in the forest area defined by coordinates. The crew then defines a sample plot by measuring individual trees located within one or multiple constructed inclusion circles around the sample point $x$, and aggregating their characteristics (e.g., timber volumes) to local plot densities (e.g., the timber density in m$^3$/ha). The estimators implemented in \pkg{forestinventory} use the so called infinite population approach in order to bridge this inventory process to the mathematics behind the estimators. This approach assumes that the spatial distribution of the local density, $Y(x)$, over the forest area is determined by a fixed piecewise constant function, as visualized in Fig. \ref{fig:inf_pop_apr}. The population total of the target variable (e.g., the total timber volume of the forest) is mathematically equivalent to the integral of that density function, which is depicted in Fig. \ref{fig:inf_pop_apr} as the volume under the density surface. From this perspective, the practical challenge is that the form of this function is unknown. Theoretically, we could get the total timber volume by observing the function value, i.e., the local density $Y(x)$, at each possible point $x$ over the forest area and taking their sum. However, this is impossible because there is an infinite number of points in the forest area. Our strategy is thus to take a sample of points, $s_2$, from an infinite population of possible points and use their associated local densities, i.e., $Y(x)$, to estimate the integral $Y=\frac{1}{\lambda(F)}\int_{F}Y(x)dx$ with $\hat{Y}=\frac{1}{n_2}\sum_{x \in s_2}Y(x)$.  The total timber volume can then be obtained by multiplying $\hat{Y}$ by the surface area of the forest, $\lambda(F)$.  All estimators included in \pkg{forestinventory} rest upon this theoretical perspective. The key point in the infinite population approach is that a local density value $Y(x)$ is associated with the sample point $x$, which constitutes the sample unit, and not with the sample plot area. This has some theoretical advantages over the finite population approach, where the sample units are the actual plot areas usually assumed to be either circular or rectangular.  This is mainly due to the impossibility of a perfect tessellation over an amorphous forest area by any choice of plot shape. Hence, the population in the finite approach is, strictly speaking, not well defined with respect to the forest area. The consideration of an underlying infinite population of sample points will also play an important role when incorporating auxiliary information in the frame of two- and three-phase estimation methods.

@@

\begin{figure}[htb]
	\begin{subfigure}[t]{0.5\textwidth}
		\centering
    \resizebox{1\hsize}{!}{\includegraphics{fig/phases_graphic(new).eps}}%
		\caption{} \label{fig:concmphase_and_sae_a}
		\end{subfigure}
	\begin{subfigure}[t]{0.5\textwidth}
		\centering
	 \resizebox{0.58\hsize}{!}{\includegraphics{fig/sae_graphic.PNG}}%
		\caption{} \label{fig:concmphase_and_sae_b}
	\end{subfigure}
\caption{(a) Concept of multiphase sampling. The square represents the forest area for which an inventory is being conducted. The points denote the sample locations $x$. Filled points indicate available information. (b) Illustration of the small area estimation problem.}
\label{fig:concmphase_and_sae}
\end{figure}

@@

The subject of model selection gets a lot of attention in the field of forest inventory. This is why it is important to understand that the mathematical interpretation of how a model is used to produce estimates is fundamentally different between the design-based and model-dependent approach. In the model-dependent (also known as model-based) framework, the sample locations $x$ are fixed and the observation $Y(x)$ taken at location $x$ is assumed to be a random variable as the forest is assumed to be the realization of a stochastic process. Although the model does not need to be fit from a probability sample, i.e., the sample locations could arbitrarily be chosen, the model should adequately describe the underlying stochastic process in order to efficiently ensure unbiased results. In practice this means that special attention must be made to ensure that the variable selection is appropriate to avoid overfitting, important variables are not omitted and all model assumptions are reasonably met through empirical verification. If a model is misspecified then estimation based on inference from that model may not be reliable. In the model-dependent framework one thus has to trust the model. In contrast, the design-based approach, on which all \pkg{forestinventory} estimators are based, rests upon the randomization of the sample locations $x$. While the sample locations $x$ are independently and uniformly distributed in the forest, the forest itself and thus the values of the local densities $Y(x)$ at any location $x \in F$ are fixed and not the result of a stochastic process. A selected observation $Y(x)$ still remains a random variable, but solely due to the random sample mechanism. A consequence of this approach is that the estimation properties of design-based regression estimators (e.g., unbiasedness) typically hold regardless of the model that is chosen. The philosophy of the design-based approach is thus to use prediction models to improve the efficiency of the estimators without having to rely on their correct specification, which makes them very attractive to be used in official statistics. They are therefore also referred to as model-assisted. It should be noted that the randomization of sample locations upon which design-based inference depends, is in practice often replaced by systematic grids to minimize travelling costs in the terrestrial survey. However, there is reasonable evidence that softening this assumption is acceptable for point and variance estimation as long as the grid does not interact with periodic features in the forest structure \citep{mandallaz2008}. The variance will in most cases be slightly overestimated and lead to wider, more conservative confidence intervals \citep{mandallaz2013a}.

@@

In the \pkg{forestinventory} package, estimators for two-phase and three-phase sampling are applied with the \code{twophase()} and \code{threephase()} functions. From these two overall function calls, various estimators for specific inventory scenarios under the chosen sampling design can be applied (Fig. \ref{fig:struct_package}). Choosing an estimator follows a tree-like structure which can serve the user as a guideline throughout this article as well as in future applications. The basic decision to make is whether an estimate and its variance should be computed for an entire inventory area (global estimators) or only for subregions of the entire inventory area (small area estimators). In the second case, the package offers three small area estimators that will in detail be described in the following sections. The estimators are available under exhaustive and non-exhaustive use of the auxiliary data. Additionally, the package also can calculate one-phase estimates solely based on terrestrial samples. All estimators are also available for cluster sampling, in which case a sample unit consists of multiple, spatially agglomerated samples. The following sections describe the mathematical details and the application of the multi-phase estimators implemented in the \proglang{R} package \pkg{forestinventory}. While \cite{mandallaz2008, mandallaz2013techa, mandallaz2013techb,mandallaz2015tech} provides an extensive derivation of all estimators, we will provide the mathematical formulas that are actually implemented in the package. We will also restrict discussion to simple sampling, while the formulas for cluster sampling are available in the technical reports \citep{mandallaz2016, mandallaz2013techa, mandallaz2013techb}. A special case under cluster sampling is described in Section \ref{sec:speccas_and_scen}.

>>>>

Most forest inventories gather terrestrial information by sending field crews to randomly (or systematically) selected points in the forest area defined by coordinates. The crew then defines a sample plot by measuring individual trees located within one or multiple constructed inclusion circles around the sample point $x$, and aggregating their characteristics (e.g., timber volumes) to local plot densities (e.g., the timber density in m$^3$/ha). The estimators implemented in \pkg{forestinventory} use the so called infinite population approach in order to bridge this inventory process to the mathematics behind the estimators. This approach assumes that the spatial distribution of the local density, $Y(x)$, over the forest area is determined by a fixed piecewise constant function, as visualized in Fig. \ref{fig:inf_pop_apr}. The population total of the target variable (e.g., the total timber volume of the forest) is mathematically equivalent to the integral of that density function, which is depicted in Fig. \ref{fig:inf_pop_apr} as the volume under the density surface. From this perspective, the practical challenge is that the form of this function is unknown. Theoretically, we could get the total timber volume by observing the function value, i.e., the local density $Y(x)$, at each possible point $x$ over the forest area and taking their sum. However, this is impossible because there is an infinite number of points in the forest area. Our strategy is thus to take a sample of points, $s_2$, from an infinite population of possible points and use their associated local densities $Y(x)$ to estimate the integral $Y=\frac{1}{\lambda(F)}\int_{F}Y(x)dx$ with $\hat{Y}=\frac{1}{n_2}\sum_{x \in s_2}Y(x)$.  The total timber volume can then be obtained by multiplying $\hat{Y}$ by the surface area of the forest, $\lambda(F)$.  All estimators included in \pkg{forestinventory} rest upon this theoretical perspective. The key point in the infinite population approach is that a local density value $Y(x)$ is associated with the sample point $x$, which constitutes the sample unit, and not with the sample plot area. This has some theoretical advantages over the finite population approach, where the sample units are the actual plot areas usually assumed to be either circular or rectangular.  This is mainly due to the impossibility of a perfect tessellation over an amorphous forest area by any choice of plot shape. Hence, the population in the finite approach is, strictly speaking, not well defined with respect to the forest area. The consideration of an underlying infinite population of sample points will also play an important role when incorporating auxiliary information in the frame of two- and three-phase estimation methods.

@@

\begin{figure}[htb]
	\begin{subfigure}[t]{0.5\textwidth}
		\centering
    \resizebox{1\hsize}{!}{\includegraphics{fig/phases_graphic(new).eps}}%
		\caption{} \label{fig:concmphase_and_sae_a}
		\end{subfigure}
	\begin{subfigure}[t]{0.5\textwidth}
		\centering
	 \resizebox{0.58\hsize}{!}{\includegraphics{fig/sae_graphic.PNG}}%
		\caption{} \label{fig:concmphase_and_sae_b}
	\end{subfigure}
\caption{(a) Concept of multi-phase sampling. The square represents the forest area for which an inventory is being conducted. The points denote the sample locations $x$. Filled points indicate available information. (b) Illustration of the small area estimation problem.}
\label{fig:concmphase_and_sae}
\end{figure}

@@

The subject of model selection gets a lot of attention in the field of forest inventory. This is why it is important to understand that the mathematical interpretation of how a model is used to produce estimates is fundamentally different between the design-based and model-dependent approach. In the model-dependent (also known as model-based) framework, the sample locations $x$ are fixed and the observation $Y(x)$ taken at location $x$ is assumed to be a random variable as the forest is assumed to be the realization of a stochastic process. Although the model does not need to be fit from a probability sample, i.e., the sample locations could arbitrarily be chosen, the model should adequately describe the underlying stochastic process in order to efficiently ensure unbiased results. In practice this means that special attention must be made to ensure that the variable selection is appropriate to avoid overfitting, important variables are not omitted and all model assumptions are reasonably met through empirical verification. If a model is misspecified then estimation based on inference from that model may not be reliable. In the model-dependent framework one thus has to trust the model. In contrast, the design-based approach, on which all \pkg{forestinventory} estimators are based, rests upon the randomization of the sample locations $x$. While the sample locations $x$ are independently and uniformly distributed in the forest, the forest itself and thus the values of the local density surface at any location $x \in F$ are fixed and not the result of a stochastic process. A selected observation $Y(x)$ still remains a random variable, but solely due to the random sample mechanism. A consequence of this approach is that the estimation properties of design-based regression estimators (e.g., unbiasedness) typically hold regardless of the model that is chosen. The philosophy of the design-based approach is thus to use prediction models to improve the efficiency of the estimators without having to rely on their correct specification, which makes them very attractive to be used in official statistics. They are therefore also referred to as model-assisted. It should be noted that the randomization of sample locations upon which design-based inference depends, is in practice often replaced by systematic grids to minimize travelling costs in the terrestrial survey. However, there is reasonable evidence that softening this assumption is acceptable for point and variance estimation as long as the grid does not interact with periodic features in the forest structure \citep{mandallaz2008}. The variance will in most cases be slightly overestimated and lead to wider, more conservative confidence intervals \citep{mandallaz2013a}.

@@

In the \pkg{forestinventory} package, estimators for two-phase and three-phase sampling are applied with the \code{twophase()} and \code{threephase()} functions. From these two overall function calls, various estimators for specific inventory scenarios under the chosen sampling design can be applied (Fig. \ref{fig:struct_package}). Choosing an estimator follows a tree-like structure which can serve the user as a guideline throughout this article as well as in future applications. The basic decision to make is whether an estimate and its variance should be computed for an entire inventory area (global estimators) or only for subregions of the entire inventory area (small area estimators). In the second case, the package offers three small area estimators that will in detail be described in the following sections. The estimators are available under exhaustive and non-exhaustive use of the auxiliary data. Additionally, the package can also calculate one-phase estimates solely based on terrestrial samples. All estimators are also available for cluster sampling, in which case a sample unit consists of multiple, spatially agglomerated samples. The following sections describe the mathematical details and the application of the multi-phase estimators implemented in the \proglang{R} package \pkg{forestinventory}. While \cite{mandallaz2008, mandallaz2013techa, mandallaz2013techb,mandallaz2015tech} provides an extensive derivation of all estimators, we will provide the mathematical formulas that are actually implemented in the package. We will also restrict discussion to simple sampling, while the formulas for cluster sampling are available in the technical reports \citep{mandallaz2016, mandallaz2013techa, mandallaz2013techb}. A special case under cluster sampling is described in Section \ref{sec:speccas_and_scen}.

### 2017-10-27 rnw/Special Cases and Scenarios.Rnw
formatting revision (2)
formatting revision (4)

A special case of multi-phase regression estimators is post-stratification, which can further be divided into the cases of multi-phase sampling for stratification and multi-phase sampling for regression within strata. Both imply the use of one or more categorical variables in the regression model(s), leading to classical ANOVA and ANCOVA models.

@@

The variance of all model-assisted estimators included in \pkg{forestinventory} can be decreased by reducing the sum of square residuals of the regression model. In case of post-stratification, this particularly implies minimizing the within strata residual square sum. Also, for post-stratification, the g-weight variance should be trusted over the external variance because it has the advantage that the strata weights are estimated from the large sample rather than the terrestrial sample $s_2$.

@@

For small area applications, the scenario might occur where the points of a cluster at sample locations $x$ spread over more than one small area, i.e., only a subset $M_{G}(x) < M(x)$ is included in the small area of interest. In this case, the zero mean residual property within the small area, $\frac{\sum_{x \in s_{2,G}}M(x)\hat{R}_{c}(x)}{\sum_{x \in s_{2,G}}M(x)}=0$, is no longer guaranteed when using the extended and pseudo extended synthetic estimator (see EXTSYNTH and EXTPSYNTH in Sections \ref{sec:twophase_sae} and \ref{sec:threephase_sae}). In this case, it is adviseable to use the (pseudo) small area estimator (PSMALL) where the zero mean residual property is still ensured.

In order to keep track of such cases, \pkg{forestinventory} tells the user to do so by returning a warning message:
<<echo=FALSE>>=
extpsynth.clust <- twophase(formula = basal ~ stade + couver + melange, data=zberg,
                     phase_id = list(phase.col = "phase_id_2p", terrgrid.id = 2),
                      cluster = "cluster",
                      small_area = list(sa.col = "ismallold", areas = c("1"),
                                        unbiased = TRUE))
@
\begin{small}
\begin{Schunk}
\begin{Sinput}
R> extpsynth.clust <- twophase(formula = basal ~ stade + couver + melange, 
+  data = zberg, phase_id = list(phase.col = "phase_id_2p", terrgrid.id = 2),
+  cluster = "cluster",  small_area = list(sa.col = "ismallold", areas = c("1"),
+  unbiased = TRUE))
Warning message:
At least one terrestrial cluster not entirely included within small area 1.
Zero mean residual assumption for small area maybe violated.
Check mean_Rc_x_hat_G and consider alternative estimator 'psmall' 
\end{Sinput}
\end{Schunk}
\end{small}

>>>>

A special case of multi-phase regression estimation is post-stratification, which can further be divided into the cases of multi-phase sampling for stratification and multi-phase sampling for regression within strata. Both imply the use of one or more categorical variables in the regression model(s), leading to classical ANOVA and ANCOVA models.

@@

The variance of all design-based estimators included in \pkg{forestinventory} can be decreased by reducing the sum of squared residuals of the regression model. In case of post-stratification, this particularly implies minimizing the within strata residual square sum. Also, for post-stratification, the g-weight variance should be trusted over the external variance because it has the advantage that the strata weights are estimated from the large sample rather than the terrestrial sample $s_2$.

@@

For small area applications, the scenario might occur where the points of a cluster at sample locations $x$ spread over more than one small area, i.e., only a subset $M_{G}(x) < M(x)$ is included in the small area of interest. In this case, the zero mean residual property within the small area, $\frac{\sum_{x \in s_{2,G}}M(x)\hat{R}_{c}(x)}{\sum_{x \in s_{2,G}}M(x)}=0$, is no longer guaranteed when using the extended and pseudo extended synthetic estimator (see EXTSYNTH and EXTPSYNTH in Sections \ref{sec:twophase_sae} and \ref{sec:threephase_sae}). In this case, it is adviseable to use the (pseudo) small area estimator (SMALL or PSMALL) where the zero mean residual property is still ensured.

In order to keep track of such cases, \pkg{forestinventory} tells the user to do so by returning a warning message:
<<echo=FALSE>>=
extpsynth.clust <- twophase(formula = basal ~ stade + couver + melange, data=zberg,
                     phase_id = list(phase.col = "phase_id_2p", terrgrid.id = 2),
                      cluster = "cluster",
                      small_area = list(sa.col = "ismallold", areas = c("1"),
                                        unbiased = TRUE))
@

\begin{small}
\begin{Schunk}
\begin{Sinput}
R> extpsynth.clust <- twophase(formula = basal ~ stade + couver + melange, 
+    data = zberg, phase_id = list(phase.col = "phase_id_2p", terrgrid.id = 2),
+    cluster = "cluster",  small_area = list(sa.col = "ismallold", areas = c("1"),
+    unbiased = TRUE))
Warning message:
At least one terrestrial cluster not entirely included within small area 1.
Zero mean residual assumption for small area maybe violated.
Check mean_Rc_x_hat_G and consider alternative estimator 'psmall' 
\end{Sinput}
\end{Schunk}
\end{small}

### 2017-10-27 rnw/Threephase_Estimators and their Application.Rnw
formatting revision (4)

The unbiased point estimates of the SMALL and PSMALL are calculated by applying the globally derived reduced and full regression model coefficients to the small area means of the explanatory variables, and then corrected for a potential model bias in $G$ by adding the small area mean of the full model residuals, i.e., $\hat{R}_{G}(x)=Y_G(x)-\pmb{Z}_G^{\top}(x)\hat{\pmb{\beta}}_{s_2}$, to the point estimate. The difference between the mean $\hat{\bar{\pmb{Z}}}^{(0)}_{1,G}$ and the more precise or exact mean $\hat{\bar{\pmb{Z}}}^{(0)}_{0,G}$ and $\bar{\pmb{Z}}^{(0)}_{0,G}$ is again considered as a correction term likewise in the global estimation (Eq. \ref{eq:reg3p}).

>>>>

The unbiased point estimates of the SMALL and PSMALL estimator are calculated by applying the globally derived reduced and full regression model coefficients to the small area means of the explanatory variables, and then corrected for a potential model bias in $G$ by adding the small area mean of the full model residuals, i.e., $\hat{R}_{G}(x)=Y_G(x)-\pmb{Z}_G^{\top}(x)\hat{\pmb{\beta}}_{s_2}$, to the point estimate. The difference between the mean $\hat{\bar{\pmb{Z}}}^{(0)}_{1,G}$ and the more precise or exact mean $\hat{\bar{\pmb{Z}}}^{(0)}_{0,G}$ and $\bar{\pmb{Z}}^{(0)}_{0,G}$ is again considered as a correction term likewise in the global estimation (Eq. \ref{eq:reg3p}).
